Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-01 edubots_surveys.Rnw
fixes variables to use similar categories for both surveys refs #17

@@

\begin{figure}[h!tbp]
\begin{center}
<<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Provided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
%       \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
<<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Provided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
%       \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
%       \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
<<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
ggplot(survey.pilot, aes(x = Provided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())

@@

ggplot(survey.pilot, aes(x = WhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())

@@

ggplot(survey.pilot, aes(x = Telegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())

>>>>

survey.pilot %>%mutate(Discipline = ifelse(as.character(Discipline) == "No", "Other", as.character(Discipline))) %>%
  mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>%
  mutate(Discipline = ifelse(as.character(Discipline) == "Technology", "Tech/Engineering", as.character(Discipline)))->survey.pilot.Discipline

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Provided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Provided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
    \end{minipage}
    %----
    \vspace{0.2mm}
    \hspace{10mm}
    \begin{minipage}[t]{0.5\textwidth}
        \centering
<<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=

ggplot(survey.pilot.Discipline, aes(x = Provided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())

@@

ggplot(survey.pilot.Discipline, aes(x = WhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())

@@

ggplot(survey.pilot.Discipline, aes(x = Telegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
